### 2014-08-18 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: Edit to description of temperature bounds in SLCFs
Chicago: minor update following Bruns' ERB comments

\chapter{Model Description}
\label{model}
Fire Dynamics Simulator~\cite{FDS_Users_Guide} is a computational fluid dynamics (CFD) model that solves a form of the Navier-Stokes equations appropriate for low-speed, thermally driven flow with an emphasis on smoke and heat transport from fires.  Within a CFD model, the room or building is divided into small three-dimensional rectangular control volumes or computational cells.  The cells are contained together within one larger volume known as a computational domain.  The CFD model computes the density, velocity, temperature, pressure, and species concentration of the gas in each cell.  Based on the laws of conservation of mass, momentum,  and energy, the model tracks the generation and movement of fire gasses. One of the most important advantages of FDS is that it is  mathematically verified~\cite{FDS_Verification_Guide} and validated against fire test data to ensure that it provides the expected results, given sufficient input data~\cite{FDS_Validation_Guide}. A complete description of the FDS model is provided in the FDS Technical Reference Guide~\cite{FDS_Math_Guide}.

@@

Figure~\ref{fig:temp_129s} shows temperatures of at least 260~$^{\circ}$C (500~$^{\circ}$F) in the second floor rear porch and rear portion of the attic. High temperatures, between 80~$^{\circ}$C (185~$^{\circ}$F) and 200~$^{\circ}$C (390~$^{\circ}$F), also extend down to the rear entrance on the first floor. Before the interior door fails (Fig.~\ref{fig:temp_159s}), the inflow of ambient air from the open rear door reduces the temperatures near the interior doorway, but at the same time, the HRR increases because of the additional ventilation, as shown in Fig.~\ref{fig:hrr}. As shown in Fig.~\ref{fig:temp_161s}, after the second floor interior door fails, the high temperature gas that filled the rear porch flows in the direction of lower pressure (i.e., towards the front door). Note that the conditions in the attic do not appear to change.
\begin{figure}[!ht]
\includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_161}
\input{../Scripts/colorbar_std} 
\input{../Scripts/colorbar_metric}
\caption{FDS simulated temperature contours, 1~s after interior door failure.}
\label{fig:temp_161s}
\end{figure}

@@

\chapter{Discussion of Simulation Results}
\label{discussion}
The results of the FDS simulations are discussed in the following two sections. The first section addresses the results of the computational modeling as they relate to the interior hallways conditions. The second section examines the model results and observed outcomes of the fire incident as they relate to tactics discussed in recent experimental research.

@@

\chapter{Summary}
NIST's Fire Dynamics Simulator was used to provide insight into the fire dynamics within a 2~\sfrac{1}{2}~story single family structure in Chicago, IL, that resulted in the death the captain of a fire department. The fuel, fire size, and fire growth rate that were used in the FDS simulations were estimated by taking into account all of the available information including the NIOSH post-incident report~\cite{NIOSH:Bowyer}, post-incident pictures, videos, and relevant literature. This resulted in a specified source fire of 12.3~MW in the attic and rear porch of the structure. However, based on the limited ventilation conditions in the attic and enclosed porch, the FDS simulation results indicated a maximum HRR of approximately 9~MW as a result of the limited supply of oxygen.

>>>>

\chapter{Model Description}
\label{model}
Fire Dynamics Simulator~\cite{FDS_Users_Guide} is a computational fluid dynamics (CFD) model that solves a form of the Navier-Stokes equations appropriate for low-speed, thermally driven flow with an emphasis on smoke and heat transport from fires.  Within a CFD model, the room or building is divided into small three-dimensional rectangular control volumes or computational cells.  The cells are contained together within one larger volume known as a computational domain.  The CFD model computes the density, velocity, temperature, pressure, and species concentration of the gas in each cell.  Based on the laws of conservation of mass, momentum,  and energy, the model tracks the generation and movement of fire gases. One of the most important advantages of FDS is that it is  mathematically verified~\cite{FDS_Verification_Guide} and validated against fire test data to ensure that it provides the expected results, given sufficient input data~\cite{FDS_Validation_Guide}. A complete description of the FDS model is provided in the FDS Technical Reference Guide~\cite{FDS_Math_Guide}.

@@

Figure~\ref{fig:temp_129s} shows temperatures of at least 260~$^{\circ}$C (500~$^{\circ}$F) in the second floor rear porch and rear portion of the attic. In this figure, the lower temperature bound is set to 25~$^{\circ}$C (77~$^{\circ}$F), and the upper temperature bound is set to 260~$^{\circ}$C (500~$^{\circ}$F); however, these are only limits on the visualized output, and the actual simulated temperatures may exceed the lower or upper bounds. High temperatures, between 80~$^{\circ}$C (185~$^{\circ}$F) and 200~$^{\circ}$C (390~$^{\circ}$F), also extend down to the rear entrance on the first floor. Before the interior door fails (Fig.~\ref{fig:temp_159s}), the inflow of ambient air from the open rear door reduces the temperatures near the interior doorway, but at the same time, the HRR increases because of the additional ventilation, as shown in Fig.~\ref{fig:hrr}. As shown in Fig.~\ref{fig:temp_161s}, after the second floor interior door fails, the high temperature gas that filled the rear porch flows in the direction of lower pressure (i.e., towards the front door). Note that the conditions in the attic do not appear to change.
\begin{figure}[!ht]
\includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_161}
\input{../Scripts/colorbar_std} 
\input{../Scripts/colorbar_metric}
\caption{FDS simulated temperature contours, 1~s after interior door failure.}
\label{fig:temp_161s}
\end{figure}

@@

\chapter{Discussion of Simulation Results}
\label{discussion}
The results of the FDS simulations are discussed in the following two sections. The first section addresses the results of the computational modeling as they relate to the interior hallway's conditions. The second section examines the model results and observed outcomes of the fire incident as they relate to tactics discussed in recent experimental research.

@@

\chapter{Summary}
NIST's Fire Dynamics Simulator was used to provide insight into the fire dynamics within a 2~\sfrac{1}{2}~story single family structure in Chicago, IL, that resulted in the death of the captain of a fire department. The fuel, fire size, and fire growth rate that were used in the FDS simulations were estimated by taking into account all of the available information including the NIOSH post-incident report~\cite{NIOSH:Bowyer}, post-incident pictures, videos, and relevant literature. This resulted in a specified source fire of 12.3~MW in the attic and rear porch of the structure. However, based on the limited ventilation conditions in the attic and enclosed porch, the FDS simulation results indicated a maximum HRR of approximately 9~MW as a result of the limited supply of oxygen.
